---
title: "*Tanytarsus gracilentus* sample summary"
author: "Lucas A. Nell"
date: "`r format(Sys.Date(), '%d %b %Y')`"
output: 
  bookdown::pdf_document2:
      dev: pdf
      toc: false
      number_sections: false
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

suppressPackageStartupMessages({
    library(tidyverse)
    library(readxl)
    library(rgdal)
    library(broom)
    library(cowplot)
    library(viridisLite)
})


# This sets plotting device on my computer:
if (!isTRUE(getOption('knitr.in.progress')) && file.exists(".Rprofile")) {
    source(".Rprofile")
}


# From decimal degrees to UTM, assuming it's Iceland and using WGS84
to_utm <- function(.df, .lat = "lat", .lon = "long") {
    .cord.dec <- SpatialPoints(cbind(.df[[.lon]], .df[[.lat]]),
                              proj4string=CRS("+proj=longlat"))
    .cord.UTM <- spTransform(.cord.dec, CRS("+proj=utm +zone=28 ellps=WGS84"))
    .df[[.lon]] <- .cord.UTM@coords[,1]
    .df[[.lat]] <- .cord.UTM@coords[,2]
    return(.df)
}


# -------------`
# Mapping data
# -------------`
myvatn_df <- readOGR(dsn = paste0("~/Box Sync/midges/location_data/",
                                  "shapefiles/myvatn"), 
                  layer = "Myvatn_WSGUTM28") %>% 
    tidy()
trap_df <- read_csv("~/Box Sync/midges/location_data/trap_locations.csv", 
                    col_types = cols()) %>% 
    rename(long = lon) %>% 
    to_utm() %>% 
    filter(trap != "Vindbelgur")
# Iceland outline is from GADM data (version 3.6; https://gadm.org/)
iceland_df <- readOGR(dsn = paste0("~/Box Sync/midges/location_data/",
                                   "shapefiles/iceland"), 
                 layer = "gadm36_ISL_0") %>% 
    tidy() %>% 
    to_utm() %>% 
    # -----------`
    # Shown below are two ways to filter this dataset, to avoid
    # plotting islands far from shore:
    # -----------`
    # 1. You can filter out islands that are very far from shore:
    # filter(!piece %in% c(90, 133, 143, 157, 215, 244, 257, 258, 260, 262))
    # 2. Filter for just the mainland:
    filter(piece == 1)

```



# NOTE

> This file isn't updated for the potentially contaminated samples and
> for the extra samples isolated after that.







## Archived samples


```{r archive_data}

archive_pal <- viridis(7, end = 0.9)[c(6, 4, 1)]


# Sample names with successful library preps:
lib_df <- read_excel(paste0("~/Box Sync/midges/dna_extraction_sequencing/DNA/",
                            "Successful_Ives Libraries_20210927.xlsx"), 
                     col_names = c("id", "na"), skip = 1) %>% 
  select(1)


# The code below was edited to find samples that had DNA extracted:

dubs <- c("SN-1-81", "KS-2-83", "KS-2-90", "SN-2-91", "SN-2-94", "KS-2-09",
          "SN-2-13", "KS-2-14", "KS-1-15", "MyKS-19")
archive_df <-  read_excel(paste0("~/Box Sync/midges/tany_identifying/",
                                "tany_from_archive.xlsx"),
                        sheet = "data-entry") %>%
    mutate(across(ends_with(c("_year", "_month", "_day")), as.integer)) %>%
    mutate(gen = factor(gen, levels = 1:2, labels = c("spring", "summer")),
           year = factor(col_year, levels = 1977L:2015L),
           date = as.Date(paste(col_year, col_month, col_day, sep = "-")),
           date_sep = as.Date(paste(sep_year, sep_month, sep_day, sep = "-")),
           N = as.integer(num_males)) %>% 
    # NOTE: this doesn't account for combining multiple samples.
    # However, I checked, and I don't see any of these that were combined 
    # with other samples. So, the `N` values should be accurate.
    filter(biotech_id %in% lib_df$id) %>% 
    select(site, year, gen, date, N) %>%
    identity()








tany_pop_df <- read_excel(paste0("~/Box Sync/zzz-archive/2020/funding/",
                                 "ASN/Chirisl_Tany_analysis.xlsx"),
                       skip = 1,  col_names = c("year", "chir_a", "chir_b",
                                                "chir_ab", "tany_a", "tany_b")) %>%
    select(year, starts_with("tany")) %>%
    gather("gen", "N", starts_with("tany")) %>%
    mutate(year = year + ifelse(gen == "tany_a", 0, 0.5)) %>%
    arrange(year) %>%
    select(-gen) %>%
    # For purposes of plotting, I'll just say this is 0.5 instead of zero, so I can
    # log transform it:
    mutate(N = ifelse(N == 0, 0.5, N)) %>%
    # To play nice with the plot of numbers of midges through time:
    rename(date = year) %>%
    mutate(Np = (log(N) - min(log(N))) * 40 / diff(range(log(N))))


# Numbers of males through time:
archive_ts_df <- crossing(year = factor(1977L:2015L, levels = 1977L:2015L),
                          gen = factor(1:2, levels = 1:2,
                                       labels = c("spring", "summer")),
                          site = sort(unique(archive_df$site[archive_df$N > 0]))) %>%
    split(interaction(.$year, .$gen, .$site)) %>%
    map_dfr(function(.x) {
        .z <- archive_df %>%
            filter(year == .x$year, gen == .x$gen, site == .x$site)
        .N <- case_when(sum(.z$N) > 0 ~ sum(.z$N),
                        # .x$site == "SN" ~ 0L,
                        TRUE ~ NA_integer_)
        mutate(.x, N = .N)
    }) %>%
    mutate(date = as.numeric(paste(year)) + ifelse(gen == "spring", 0, 0.5),
           N = case_when(N > 40 ~ 40.0,
                         TRUE ~ N * 1.0),
           Z = factor(as.integer(N > 0), levels = 0:1)) %>%
    split(interaction(.$year, .$gen, drop = TRUE)) %>%
    map_dfr(function(.x) {
        stopifnot(nrow(.x) > 0)
        logl <- duplicated(.x$N) & !is.na(.x$N) & .x$N > 0
        if (any(logl)) {
            .x$N[logl] <- .x$N[logl] + (1:sum(logl))
        }
        return(.x)
    }) %>%
    mutate(period = case_when(date < 1990 ~ 0,
                              date < 2003 ~ 1,
                              TRUE ~ 2) %>%
               factor(levels = 0:2),
           # Convert to more accurate site names:
           site = case_when(site == "SN" ~ "Syðri Neslönd",
                            site == "KS" ~ "Kálfaströnd",
                            site == "H" ~ "Haganes",
                            site == "V" ~ "Vindbelgur",
                            TRUE ~ NA_character_))



yield_df <- read_excel("~/Box Sync/2021/midges/Picogreen_Results_20210803.xlsx") %>% 
    select(1, 5) %>% 
    set_names(c("sample", "yield")) %>% 
    mutate(year = str_sub(sample, -2, -1),
           year = ifelse(year >= 77, paste0("19", year),
                         paste0("20", year)) %>% 
               as.integer(),
           site = str_sub(sample, 1, 2) %>% str_remove("-")) %>% 
    mutate(site = case_when(site == "SN" ~ "Syðri Neslönd",
                            site == "KS" ~ "Kálfaströnd",
                            site == "H" ~ "Haganes",
                            TRUE ~ NA_character_)) %>% 
    filter(!is.na(site)) %>% 
    mutate(site = factor(site, levels = c("Syðri Neslönd", "Kálfaströnd", 
                                          "Haganes")),
           gen = str_sub(sample, -4, -4) %>% as.integer(),
           date = year + ifelse(gen == 1, 0, 0.5)) %>% 
    arrange(date, site)


# 1.	1981 gen 1 (yield = 5.54 ng)
# 2.	1983 gen 2 (yield = 4.23 ng)
# 3.	1990 gen 2 (yield = 5.54 ng)
# 4.	1991 gen 2 (yield = 4.88 ng)
# 5.	1994 gen 2 (yield = 2.28 ng)
# 6.	2009 gen 2 (yield = 4.23 ng)
# 7.	2013 gen 2 (yield = 2.28 ng)
# 8.	2014 gen 2 (yield ≈ 0 ng)
# 9.	2015 gen 1 (yield ≈ 0 ng)







plot_mod <- function(.df) {
    .df %>%
        mutate(resample = (year == 1981 & gen == 1) |
                   (year == 1983 & gen == 2) |
                   (year == 1990 & gen == 2) |
                   (year == 1991 & gen == 2) |
                   (year == 1994 & gen == 2) |
                   (year == 2009 & gen == 2) |
                   (year == 2013 & gen == 2) |
                   (year == 2014 & gen == 2) |
                   (year == 2015 & gen == 1)) %>% 
        mutate(cutoff = case_when(yield >= 10 ~ "above cutoff",
                                  TRUE ~ "below cutoff") %>% 
                   factor(levels = c("above cutoff", "below cutoff")),
               yield = ifelse(yield > 10, 10, yield),
               yield = ifelse(yield < 0, 0, yield),
               period = case_when(date < 1990 ~ 0,
                                  date < 2003 ~ 1,
                                  TRUE ~ 2) %>%
                   factor(levels = 0:2),
               N = case_when(site == "Haganes" ~ 12.5,
                             site == "Kálfaströnd" ~ 12.5 + 2,
                             TRUE ~ 12.5 + 2 * 2)
        )
}


yield_df %>% 
    plot_mod() %>% 
    ggplot(aes(date, N)) +
    geom_area(data = tany_pop_df %>%
                  mutate(period = case_when(date < 1990 ~ 0,
                                            date < 2003 ~ 1,
                                            TRUE ~ 2) %>%
                             factor(levels = 0:2),
                         N = log1p(N)),
              fill = "gray90") +
    geom_vline(data = tibble(date = map(1977:2015, ~ .x + c(0, 0.5)) %>%
                                 do.call(what = c)) %>%
                   mutate(period = case_when(date < 1990 ~ 0,
                                             date < 2003 ~ 1,
                                             TRUE ~ 2) %>%
                              factor(levels = 0:2)),
               aes(xintercept = date), color = "gray70") +
    geom_label(data = yield_df %>% 
                   plot_mod() %>% 
                   filter(resample) %>% 
                   distinct(date, period) %>% 
                   mutate(N = 10, lab = 1:n()),
               aes(label = lab), 
               size = 12 / 2.83465, vjust = 0) +
    geom_point(aes(fill = yield, color = cutoff, shape = site),
               size = 3) +
    facet_wrap(~ period, nrow = 3, scales = "free_x") +
    theme_minimal() +
    scale_x_continuous("Date", breaks = seq(1978, 2014, 2)) +
    ylab("log(N)") +
    scale_color_manual(NULL, values = c("black", "red")) +
    scale_shape_manual(NULL, values = c(23, 24, 22)) +
    scale_fill_gradient(low = "white", high = "black", 
                        breaks = seq(0, 10, 2.5),
                        labels = c(seq(0, 7.5, 2.5), "≥10")) +
    guides(color = guide_legend(override.aes = list(shape = 1)),
           shape = guide_legend(override.aes = list(color = "black", fill = NA, 
                                                    size = 3))) +
    theme(strip.text = element_blank())




yield_df %>% 
    mutate(period = case_when(date < 1990 ~ 0,
                              date < 2003 ~ 1,
                              TRUE ~ 2) %>%
               factor(levels = 0:2),
           N = case_when(yield > 10 ~ 10,
                         yield < 0 ~ 0,
                         TRUE ~ yield)
           ) %>% 
    ggplot(aes(date, N)) +
    geom_vline(data = tibble(date = map(1977:2015, ~ .x + c(0, 0.5)) %>%
                                 do.call(what = c)) %>%
                   mutate(period = case_when(date < 1990 ~ 0,
                                             date < 2003 ~ 1,
                                             TRUE ~ 2) %>%
                              factor(levels = 0:2)),
               aes(xintercept = date), color = "gray70") +
    # geom_area(data = tany_pop_df %>%
    #               mutate(period = case_when(date < 1990 ~ 0,
    #                                         date < 2003 ~ 1,
    #                                         TRUE ~ 2) %>%
    #                          factor(levels = 0:2),
    #                      N = (log(N) - min(log(N))) * 10 / diff(range(log(N)))),
    #           fill = "gray90") +
    geom_point(aes(color = site)) +
    facet_wrap(~ period, nrow = 3, scales = "free_x") +
    theme_minimal() +
    scale_x_continuous("Date", breaks = seq(1978, 2014, 2)) +
    ylab("log(N)") +
    scale_color_manual(NULL, values = archive_pal)


```



From the time series from 1977--2015, I extracted at least 
10 *Tanytarsus gracilentus* individuals from
`r archive_df %>% filter(N >= 10) %>% nrow()` samples
(Figure \@ref(fig:archive)A).
These samples span
`r archive_df %>% filter(N >= 10) %>% distinct(year, gen) %>% nrow()` 
of the 78 possible generations.
I chose 10 as a fairly arbitrary cutoff to prevent issues with having 
low numbers of individuals in a sequencing pool.
These include an increased chance of bias associated 
with unequal amounts of DNA from each individual and 
with non-random sampling of individuals from the population.
Where we didn't have enough individuals from our primary site, Syðri Neslönd,
I pulled samples from either Haganes or Kálfaströnd
(Figure \@ref(fig:archive)B).
I extracted individuals from multiple sites for 
`r archive_df %>% filter(N >= 10) %>% group_by(year, gen) %>% summarize(N = length(unique(site)), .groups = "drop") %>% filter(N > 1) %>% nrow()`
generations, which should help inform whether the Lake Mývatn population of
*T. gracilentus* is as panmictic as we think.






```{r archive_cap}
archive_p_cap <- paste("Sample summary for archived samples.",
                       "(A) Number of *Tanytarsus gracilentus* individuals",
                       "separated from each generation and site's original",
                       "mixed-species sample.",
                       "Solid points indicate samples I plan to sequence",
                       "(those with at least 10 individuals), and",
                       "hollow points are samples I don't plan to sequence.",
                       "Lines connect consecutive points from the same site.",
                       "The gray shaded region indicates the log-transformed",
                       "*T. gracilentus* abundance at Syðri Neslönd.",
                       "(B) A map of the different sites at Lake Mývatn.",
                       "(A,B) Color indicates site.")
```
```{r archive, fig.height=4, fig.width=6.5, fig.cap=archive_p_cap}

archive_ts_p <- archive_ts_df %>%
    # filter(N > 0) %>% 
    ggplot(aes(date, N)) +
    geom_area(data = tany_pop_df %>%
                  mutate(period = case_when(date < 1990 ~ 0,
                                            date < 2003 ~ 1,
                                            TRUE ~ 2) %>%
                             factor(levels = 0:2)),
              aes(y = Np),
              fill = "gray90") +
    geom_vline(data = tibble(date = map(1977:2015, ~ .x + c(0, 0.5)) %>%
                                 do.call(what = c)) %>%
                   mutate(period = case_when(date < 1990 ~ 0,
                                             date < 2003 ~ 1,
                                             TRUE ~ 2) %>%
                              factor(levels = 0:2)),
               aes(xintercept = date), color = "gray70") +
    # geom_hline(yintercept = 10, color = "gray70", linetype = 2) +
    geom_point(aes(color = site), na.rm = TRUE) +
    # geom_point(data = archive_ts_df %>% filter(N == 0),
    #            aes(color = site), shape = 4, na.rm = TRUE) +
    geom_line(aes(color = site), na.rm = TRUE) +
    facet_wrap(~ period, nrow = 3, scales = "free_x") +
    scale_shape_manual(values = c(1, 19), guide = "none") +
    # scale_color_manual(values = c("dodgerblue", "firebrick", "gray30")) +
    # scale_color_brewer(NULL, palette = "Dark2") +
    scale_color_manual(NULL, values = archive_pal, guide = "none") +
    scale_x_continuous(breaks = seq(1978, 2014, 2)) +
    ylab("Number of individuals") +
    theme_classic() +
    theme(strip.background = element_blank(),
          strip.text = element_blank(),
          axis.title.x = element_blank(), 
          legend.position = "right")


myvatn_map <- myvatn_df %>%
    ggplot(aes(x = long, y = lat)) +
    geom_polygon(aes(group = group, fill = hole), color = "black", size = 0.1) +
    geom_point(data = trap_df, aes(color = trap), size = 4) +
    geom_segment(data = tibble(longe = 405e3, long = longe - 1e3, lat = 7280e3),
                 aes(xend = longe, yend = lat), size = 1) +
    geom_text(data = tibble(lat = 7280e3 + 200,  long = 405e3-500),
              label = "1 km", vjust = 0, hjust = 0.5, size = 10 / 2.83465) +
    scale_fill_manual(values = c("lightblue", "white"), guide = "none") +
    # scale_color_brewer(NULL, guide = FALSE, palette = "Dark2") +
    scale_color_manual(NULL, values = archive_pal) +
    guides(color = guide_legend(override.aes = list(shape = 19, size = 3))) +
    coord_equal() +
    theme_minimal() +
    theme(axis.title = element_blank(),
          axis.text = element_blank(),
          axis.ticks = element_blank(),
          panel.grid = element_blank()) +
    NULL


archive_legend <- get_legend(myvatn_map)

archive_p <- plot_grid(archive_ts_p, 
                       plot_grid(myvatn_map + theme(legend.position = "none"), 
                                 archive_legend, ncol = 1,
                                 rel_heights = c(1, 0.5)), 
                       labels = LETTERS[1:2],
                       rel_widths = c(1, 0.5), label_fontface = "plain")

# # To test for proper sizing:
# ggsave("~/Desktop/archive_plot.pdf", archive_p, width = 6.5, height = 4)

archive_p

```



\clearpage


## Other lakes

```{r lakes_data}
all_lake_samples <- read_excel("~/Box Sync/2020/midges/tany_other_lakes.xlsx",
                               sheet = "all-samples", na = c("", "NA")) %>% 
    select(lake, sample, month, day, lat, lon) %>% 
    mutate(month = map_int(month, ~ which(month.name == .x)),
           date = as.Date(sprintf("2019-%i-%i", month, day)))
lakes_df <- read_excel("~/Box Sync/2020/midges/tany_other_lakes.xlsx",
                       sheet = "data-entry") %>% 
    select(lake, sample, col_month, col_day, n_tany) %>% 
    rename(month = col_month, day = col_day) %>% 
    filter(n_tany > 0) %>% 
    # Had to add this bc in the "all-samples" sheet, before June 20th, 
    # when only a single sample was taken from a site on a particular day, 
    # I called it sample # 1.
    # After June 20th, I just left it blank.
    # In the "data-entry" sheet, I just always left these blank.
    mutate(sample = ifelse(is.na(sample) & month == 6 & day < 20, 
                           1, sample)) %>%
    left_join(all_lake_samples %>% select(-date),
              by = c("lake", "sample", "month", "day")) %>% 
    # "Blonduos" is the lake's nearest town; the lake is "Grafarvatn"
    mutate(lake = ifelse(lake == "Blonduos", "Grafarvatn", lake)) %>% 
    # To account for combining from Myvatn - SN
    group_by(lake, month, day) %>% 
    summarize(n_tany = sum(n_tany), 
              lat = mean(lat),
              long = mean(lon),
              .groups = "drop") %>% 
    to_utm() %>% 
    mutate(tany_num_f = ifelse(n_tany >= 40, 1, 0) %>% factor())
```


From `r format(min(all_lake_samples$date), '%d %b %Y')` through
`r format(max(all_lake_samples$date), '%d %b %Y')`, I sampled 
`r (all_lake_samples$lake %>% unique() %>% length()) - 3` lakes outside Mývatn, 
of which `r (lakes_df$lake %>% unique() %>% length()) - 3` yielded
*T. gracilentus* (Figure \@ref(fig:lakes)).
I also sampled 3 sites at Lake Mývatn (see inset; all yielded *T. gracilentus*).
Most of these samples are on the north coast, but I was able to get a
couple in the SW corner near/within Reykjavík and another
near Snæfellsjökull in the west.
Only 4 of the samples yielded < 40 individuals, but 
I vote that we still sequence them all separately.








```{r lakes_cap}
lakes_p_cap <- paste("Map of lakes with *Tanytarsus gracilentus* sampled in",
                     "spring 2019.",
                     "Blue points indicate lakes where at least 40 individual",
                     "*T. gracilentus* were sampled.",
                     "Points in red represent lakes with < 40, and the",
                     "nearby number indicates how many.",
                     "The inset shows the samples taken from Lake Mývatn.")
```

```{r lakes, fig.height=4.5, fig.width=6.5, fig.cap=lakes_p_cap}



lakes_iceland_p <- iceland_df %>%
    ggplot(aes(x = long, y = lat)) +
    geom_polygon(aes(group = group), color = "black", size = 0.1, 
                 fill = "gray80") +
    geom_point(data = lakes_df %>% filter(!grepl("Mývatn", lake)), 
               aes(color = tany_num_f), size = 3) +
    geom_text(data = lakes_df %>% 
                  filter(n_tany < 40) %>% 
                  arrange(lake) %>% 
                  mutate(long = long + c(0, 0, -15, 0) * 1e3,
                         lat = lat + c(-10, -10, 5, -10) * 1e3), 
              aes(color = tany_num_f, label = n_tany), size = 8 / 2.83465,
              vjust = 1, hjust = 0.5) +
    geom_rect(data = tibble(x = 403118.1 - 100, xe = 411932.0 + 100, 
                            y = 7271491 - 100, ye = 7282704 + 100),
              aes(xmin = x, xmax = xe, ymin = y, ymax = ye), 
              inherit.aes = FALSE, size = 0.75, fill = NA, color = "black") +
    scale_color_manual(values = c("firebrick1", "dodgerblue"), guide = FALSE) +
    coord_equal() +
    theme_minimal() +
    theme(axis.title = element_blank(),
          axis.text = element_blank(),
          axis.ticks = element_blank(),
          panel.grid = element_blank()) +
    NULL


lakes_myvatn_p <- myvatn_df %>%
    ggplot(aes(x = long, y = lat)) +
    geom_rect(data = tibble(x = 403118.1 - 100, xe = 411932.0 + 100, 
                            y = 7271491 - 100, ye = 7282704 + 100),
              aes(xmin = x, xmax = xe, ymin = y, ymax = ye), 
              inherit.aes = FALSE, size = 0.75, fill = "white", color = "black") +
    geom_polygon(aes(group = group, fill = hole), color = "black", size = 0.1) +
    geom_point(data = lakes_df %>% filter(grepl("Mývatn", lake)), 
               size = 4, color = "dodgerblue3") +
    geom_segment(data = tibble(longe = 405e3, long = longe - 1e3, lat = 7280e3),
                 aes(xend = longe, yend = lat), size = 1) +
    geom_text(data = tibble(lat = 7280e3 + 200,  long = 405e3-500),
              label = "1 km", vjust = 0, hjust = 0.5, size = 10 / 2.83465) +
    scale_fill_manual(values = c("lightblue", "white"), guide = FALSE) +
    coord_equal(xlim = c(403118.1 - 100, 411932.0 + 100),
                ylim = c(7271491 - 100, 7282704 + 100)) +
    theme_minimal() +
    theme(axis.title = element_blank(),
          axis.text = element_blank(),
          axis.ticks = element_blank(),
          panel.grid = element_blank()) +
    NULL



lakes_p <- ggdraw() +
  draw_plot(lakes_iceland_p) +
  draw_plot(lakes_myvatn_p, x = 0.75, y = 0.0, width = 0.25, height = 0.5)


# # To test for proper sizing:
# ggsave("~/Desktop/lakes_plot.pdf", lakes_p, width = 6.5, height = 4.5)

lakes_p

```




## Map of Paracladopelma laminata


```{r lakes_data}

all_lake_samples <- read_excel(paste0("~/Box Sync/midges/tany_identifying/",
                                      "tany_other_lakes.xlsx"),
                               sheet = "all-samples", na = c("", "NA")) %>% 
    select(lake, sample, month, day, lat, lon) %>% 
    mutate(month = map_int(month, ~ which(month.name == .x)),
           date = as.Date(sprintf("2019-%i-%i", month, day)))

p_lam_df <- read_excel(paste0("~/Box Sync/midges/tany_identifying/",
                                      "tany_other_lakes.xlsx"),
                               sheet = "data-entry") %>% 
    filter(grepl("laminata", other_spp)) %>% 
    select(lake, sample, col_month, col_day, n_tany) %>% 
    rename(month = col_month, day = col_day) %>% 
     mutate(sample = ifelse(is.na(sample) & month == 6 & day < 20, 
                           1, sample)) %>%
    left_join(all_lake_samples %>% select(-date),
              by = c("lake", "sample", "month", "day")) %>% 
    # "Blonduos" is the lake's nearest town; the lake is "Grafarvatn"
    mutate(lake = ifelse(lake == "Blonduos", "Grafarvatn", lake)) %>% 
    rename(long = lon) %>% 
    to_utm()


iceland_df %>%
    ggplot(aes(x = long, y = lat)) +
    geom_polygon(aes(group = group), color = "black", size = 0.1, 
                 fill = "gray80") +
    geom_point(data = all_lake_samples %>% 
                   group_by(lake) %>% 
                   summarize(lat = mean(lat, na.rm=TRUE), 
                             long = mean(lon, na.rm=TRUE), 
                             .groups = "drop") %>% 
                   to_utm(), 
               size = 2, color = "firebrick") +
    geom_point(data = p_lam_df, size = 3, color = "dodgerblue") +
    coord_equal() +
    theme_minimal() +
    theme(axis.title = element_blank(),
          axis.text = element_blank(),
          axis.ticks = element_blank(),
          panel.grid = element_blank()) +
    NULL


```
